Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
revise some text

For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. Throughout the text, we do not make comparisons when their outcome would depend on our decision to quantify diversity effects on a log-scale of oxygen diffusivity. For example, we compare the direction but not the magnitude of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). On a logarithmic scale, the magnitude of these diversity effects depends on whether a tipping point is located at low or high oxygen diffusivity (Figure 13.1) and therefore on whether a group dominates the oxic or the anoxic state.

>>>>

For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. In our work, we only make comparisions where the outcome is the same when a log- or and arithmetic-scale of oxygen diffusivity was used. For example, compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). The direction of the effects does not depend on the log/arithmetic scale decision.

In contrast, we avoid comparisons where the outcome would differ when a log- or and arithmetic-scale of oxygen diffusivity was used. An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-anoxic transition. We avoid this comparison of magnitudes because with a log scale the diversity effect is larger for the oxic-anoxic transition (Figure \@ref(fig:fig-log-nonlog)n), while on an arithmetic scale the diversity effect is larger for the anoxic-oxic transition (Figure \@ref(fig:fig-log-nonlog)o).
